---
title: "About us"
description: |
  Warwick R-user group is for everybody interested in R, the programming language for statistical computing, data science, visualisation and reproducible reporting.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
```

Warwick R User Group meets every 2 months to discuss R-related topics. At each session, speakers present interesting R packages (and how to make your own), share tips and tricks and offer advice to new R users.

Everyone is welcome, regardless of R programming experience, from across or outside Warwick University. For further information, visit our Meetup.com page or contact a member of the [WRUG committee](about#committee).

## Committee

::: {.people-gallery}

::: {#person1}
```{r, results = "asis"}
person_info(name = "Carlos Camara Menoyo")
```
:::

::: {#person2}
```{r, results = "asis"}
person_info(name = "Aditi Shenvi")
```
:::

::: {#person3}
```{r, results = "asis"}
person_info(name = "Chris Mainey")
```
:::

::: {#person4}
```{r, results = "asis"}
person_info(name = "James Tripp")
```
:::

::: {#person5}
```{r, results = "asis"}
person_info(name = "Heather Turner",
            pic = "media/heather_turner.jpg",
            alt = "Heather Turner outside in the sun, smiling. She is a white woman in her 40s with dark straight hair tied back and wears glasses.",
            website = "https://warwick.ac.uk/heatherturner",
            email = "h.turner.1@warwick.ac.uk")
```
:::

:::




## Support

<img src= "https://www.r-consortium.org/wp-content/uploads/sites/13/2016/09/RConsortium_Horizontal_Pantone.png" alt = "R Consortium Logo">

Warwick R User Group is supported by the [R Consortium](https://www.r-consortium.org/).
We follow the R Consortium [R Community code of conduct](https://wiki.r-consortium.org/view/R_Consortium_and_the_R_Community_Code_of_Conduct).